Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-01-18 Thesis/chapter/060-results-material.tex
finished XRD

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific and Pre-optimization}
\label{sec:res-mat}
%\subsubsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \ch{H2SO4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers there was no clear improvement and the results reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure \ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \caption{SEM picture of \gls{zro} produces by H2O solution} \label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{SEM picture of \gls{zro} produced by buoh solution} \label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 1x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
    \end{subfigure}
    \caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d)} \label{fig:sem}
\end{figure}

%%%%%%%%% CROSS SECTION
Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
%
Measuring the cross section on steel was not as straight forward because of the ductility of steel. 
The only way to get an insight into the thickness of the layer via \gls{sem} was through 
scratching the surface with an diamond glass cutter. 
The result can be seen in figure \ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be around \um{1}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{SEM}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Spectrometry}

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{Reflectance of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
    \caption{\td{UVVisIR}} \label{fig:ir}
\end{figure}

In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers the more of the light is absorbed (1000nm) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is the more wavy the graph, which most likely can be attributed to interference.
This trend can also be observed in figure \ref{fig:ir-gr}.
The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
%\fi

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where ordinate shows the logarithm to the base of 10 of the absolute value of the current. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
but was not investigated further. 
Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
%
\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}

Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
\td{why cubic \gls{zro} when cubic stable above 2270C? todo: find xrd of monoclinic and tetragonal}
%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
%This wideness is is due to polycrystalline form of the material which is expected 
%due to the sol-gel creation process and multiple applications of layers. 
%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.

>>>>

In this section the results will pe presented, explained and discussed. 
Starting with physical measurements and material properties. 
Followed by the presentation and exploration of the results obtain by optimisation/exploration  with the \gls{emma} method. 
Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific and Pre-optimization}
\label{sec:res-mat}
%\subsubsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, there was no improvement and the results reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure \ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \caption{SEM picture of \gls{zro} produces by H2O solution} \label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{SEM picture of \gls{zro} produced by buoh solution} \label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 5x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
        \caption{150 steel 2Fx5} \label{fig:sem-cs2}
    \end{subfigure}
	\caption{SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} \label{fig:sem}
\end{figure}

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and no more used for \gls{db}. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution \td{what is this aging process chemically? oxidation, hydrolisation?}.
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

%%%%%%%%% CROSS SECTION
Figure \ref{fig:sem-cs1} shows the cross section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
Resorting to scratching the surface with an diamond glass cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure \ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the magnitude of \um{1}.

\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
In addition, two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
%
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ (highest to lowest intensity) clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
They confirm that the produced substance is \gls{zro}.
To further clarify the phase Raman spectra are needed since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Spectrometry}

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmission of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{Reflection of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
	\caption{\gls{uv}/\gls{vis}/\gls{nir}} Reflection vs Reflectance and Transmission vs Transmittance\label{fig:ir}
\end{figure}

In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker, the layer is the more wavy the graph, which can be attributed to interference.
This trend can also be observed in figure \ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
%
Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the decimal logarithm of the absolute value of the current in Ampere. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
but was not investigated further. 
Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
%
\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{SEM}

@@

%\iffalse

### 2023-01-18 Thesis/chapter/062-post-emma.tex
finished XRD

\label{sec:res-post-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data

\textbf{What can/did we test?}
With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
%We tested for each input variable the influence on rho and gamma 
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
%and also as a test on vcal and $\lambda$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
to guess that in 1 out of 20 cases the results could be false positives, 
whereas the frequency is much higher. 
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
\td{could test anova on difference generation data sets}

>>>>

\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
in this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the optimization. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance/effect/correlation} 
on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data

\textbf{What can/did we test?}
With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
%We tested for each input variable the influence on rho and gamma 
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
%and also as a test on vcal and $\lambda$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
to guess that in 1 out of 20 cases the results could be false positives, 
whereas the frequency is much higher. 
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
\td{could test anova on different generations data sets}
